This statement defines a variable named invocation, which is assigned a string value that includes a call to a function named say_verbose. The string itself includes some additional text that provides information about the invocation being made.

Here is a breakdown of the statement:

invocation=: This is the variable assignment operator, which is used to assign a value to the variable named invocation.
'say_verbose "Calling: ${yellow:-}${FUNCNAME[0]} ${green:-}$*${normal:-}"': This is the value being assigned to the invocation variable. It is a single-quoted string that contains a call to the function say_verbose with a parameter. The parameter is a string that includes several variable substitutions:
${yellow:-}: This is a parameter expansion that substitutes the value of the variable yellow, or an empty string if yellow is not set.
${FUNCNAME[0]}: This is an array variable that contains the name of the current function or script. Here, it is being used to get the name of the function that is calling say_verbose.
${green:-}: This is similar to the first substitution, but it substitutes the value of the variable green.
$*: This is a special parameter that expands to the positional parameters (i.e., the arguments passed to the current script or function). Here, it is being used to include all arguments passed to the function in the string.
${normal:-}: This is similar to the first two substitutions, but it substitutes the value of the variable normal.
Overall, this statement defines a variable that contains a string that provides information about a function call, including the name of the calling function and all of its arguments. The say_verbose function is expected to print this string to the console (or some other output) with additional formatting or logging information.
